%! Author = simon
%! Date = 2/9/25

%----------------------------------------------------------------------------------------
%	DISCLAIMER/COPYRIGHT PAGE
%----------------------------------------------------------------------------------------

\thispagestyle{empty} % Suppress headers and footers on this page

\begin{twothirdswidth} % Content in this environment to be at two-thirds of the whole page width
    \footnotesize % Reduce font size

    \subsection*{Disclaimer}

    This report is intended for informational purposes only and is not intended as an offer or solicitation for the purchase or sale of any security or other financial instrument. The information contained in this report is not to be construed as investment advice. Information obtained from third-party sources is believed to be reliable, but no representations or warranty, expressed or implied, is made by FinAnalize, its affiliates or any other person to its accuracy, completeness, timeliness or correctness. FinAnalize is not responsible for the content of external sites that link to this site or which are linked from it. The information contained in this report is not to be construed as investment advice. Information obtained from third-party sources is believed to be reliable, but no representations or warranty, expressed or implied, is made by FinAnalize, its affiliates or any other person to its accuracy, completeness, timeliness or correctness. FinAnalize is not responsible for the content of external sites that link to this site or which are linked from it.
    \subsection*{Copyright}

    \textcopyright~ 2025 FinAnalize

    All rights reserved. No part of this report may be reproduced, stored in a retrieval system, or transmitted in any form or by any means, electronic, mechanical, photocopying, recording, scanning, or otherwise, except as permitted under Section 107 or 108 of the 1976 United States Copyright Act, without the prior written permission of the publisher.

    \subsection*{Contact}

    Erasmushogeschool Brussel\\
    Nijverheidskaai 170\\
    1090 Anderlecht, Belgium\\

    Contact: info@finanalize.com

\end{twothirdswidth}

